---
title: "pres1"
author: "kl"
date: "11/14/2017"
output:
  ioslides_presentation: 
    logo: logo.png
    smaller: yes
    theme: readable
    widescreen: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3
- Bullet 4
- Bullet 5

## Slide with Bullets {.smaller .build}

- *Bullet 1*
- _Bullet 2_
- **Bullet 3**
- Bullet 4
- Bullet 5

<div class="red2">
This text is red
</div>

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3
- Bullet 4
- Bullet 5

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

